Manuscript_rsfMRI

### 2020-11-03 draft_rsfmri.Rmd
result section FD model

<!-- Brain mask: FD --> Surprisingly, 
<!-- GM mask: FD -->

@@

<!-- Incomplete data --> how many had three/ two/ one time point?

>>>>

<!-- Brain mask: FD --> To investigate the unique contributions of the average value of and the longitudinal change in mean FD, we constructed a model that entailed both of the predictors as covariates of interest and only age and sex as nuisance covariates. 
Surprisingly, there was no significant effect neither for the total sample, nor for the intervention group only<!-- or for  the first two time points only -->.

<!-- GM mask: FD -->

<!-- Neurovault --> 
Contrasts images are published on NeuroVault: ......

@@

<!-- Incomplete data --> how many had three/ two/ one time point?
\newpage
